Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Mechanical Perturbations

### 2024-06-06 main.tex
Define our k_phi.

\subsection{Balance Assist Control}
%
We use a forward speed \(v\) gain scheduled proportional roll rate feedback
controller to stabilize the bicycle. The commanded steer torque
\(T^\textrm{m}_\delta\) from the steer motor follows the control law
%
\begin{align}
  T^\textrm{m}_\delta = k(v_{weave} - v)\dot{\phi}
\end{align}
%
where 4.7~\si{\meter\per\second} is the weave critical speed predicted from the
open loop bicycle rigid-rider dynamics. We use \(k=8\) and \(k=10\) as gain
values during the experiments. Scaling the proportional feedback gain linearly
with respect to speed stabilizes the normally unstable weave mode of the
bicycle from speeds of X~\si{\kilo\meter\per\hour} to
X~\si{\kilo\meter\per\hour} as shown in Figure~\ref{fig:eigenvalues}.

@@

\subsection{Measurements}
%
We measure the time histories of the Bump'Em delivered perturbation forces and
the bicycle's steer angle, roll angle, roll angular rate, and forward speed.
Figure~\ref{fig:perturbation_0} shows an example perturbation force measurement
compared to our Bump'Em controller command.
%
\begin{figure}
  \centering
  \includegraphics[width=140mm]{figures/perturbation_0.png}
  \caption{Motor force and resulting  steer torque perturbation based on an 80N
  counterclockwise applied force.}
  \label{fig:perturbation_0}
\end{figure}

>>>>

\subsection{Balance Assist Control}
%
We use a forward speed \(v\) gain scheduled proportional roll rate feedback
controller to stabilize the bicycle. The commanded steer torque
\(T^\textrm{m}_\delta\) from the steer motor follows the control law
%
\begin{align}
  T^\textrm{m}_\delta = -k_{\dot{\phi}}\dot{\phi} = k(v_{weave} - v)\dot{\phi}
\end{align}
%
where 4.7~\si{\meter\per\second} is the weave critical speed predicted from the
open loop bicycle rigid-rider dynamics. We use \(k=8\) and \(k=10\) as gain
values during the experiments. Scaling the proportional feedback gain linearly
with respect to speed stabilizes the normally unstable weave mode of the
bicycle from speeds of X~\si{\kilo\meter\per\hour} to
X~\si{\kilo\meter\per\hour} as shown in Figure~\ref{fig:eigenvalues}.

@@

\subsection{Measurements}
%
We measure the time histories of the Bump'Em delivered perturbation forces and
the bicycle's steer angle, roll angle, roll angular rate, and forward speed.
Figure~\ref{fig:perturbation_0}\todo{Maybe remove the top plot of individual
forces and add plots of roll angle, roll rate, steer rate.} shows an example
perturbation force measurement compared to our Bump'Em controller command.
%
\begin{figure}
  \centering
  \includegraphics[width=140mm]{figures/perturbation_0.png}
  \caption{Motor force and resulting  steer torque perturbation based on an 80N
    counterclockwise applied force.}
  \label{fig:perturbation_0}
\end{figure}
